PANCHANGE_data_preprocessing

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
ocir coping  missigness updates

# PHQ missigness

## retrospective
```{r PHQ retrospective missingness}
coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
  mutate(
    na_per_person_phq_retro =         # variable for NA per person
      rowSums(
        is.na(.[phq.items_retro])
      )
  )

@@

```{r PHQ retro missingness 8 items}
coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
  mutate(
    phq.missing_only_suicide_item_retro = 
      if_else(
        condition = na_per_person_phq_retro == 1 & 
          is.na(phq.dead_hurting_thoughts_retro_numeric), 
        true = 1,
        false = 0,
        missing = NA_real_
      )
  )

@@

## baseline
```{r PHQ baseline missingness}
coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
  mutate(
    na_per_person_phq_base =         # variable for NA per person
      rowSums(                       
        is.na(.[phq.items_base])
      )
  )

@@

We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
```{r PHQ base missingness 8 items}
coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
  mutate(
    phq.missing_only_suicide_item_base = 
      if_else(
        condition = na_per_person_phq_base == 1 & 
          is.na(phq.dead_hurting_thoughts_base_numeric), 
        true = 1,
        false = 0,
        missing = NA_real_
      )
  )

@@

>>>>

missigness

retrospective
```{r coping phq retro missingness}
coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
  mutate(
    na_per_person_phq_retro =         # variable for NA per person
      rowSums(
        is.na(.[phq.items_retro])
      )
  )

@@

```{r coping phq retro missingness 8 items}
coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
  mutate(
    phq.missing_only_suicide_item_retro = 
      if_else(
        condition = na_per_person_phq_retro == 1 & 
          is.na(phq.dead_hurting_thoughts_retro_numeric), 
        true = 1,
        false = 0,
        missing = NA_real_
      )
  )

@@

baseline
```{r coping phq base missingness}
coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
  mutate(
    na_per_person_phq_base =         # variable for NA per person
      rowSums(                       
        is.na(.[phq.items_base])
      )
  )

@@

We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
```{r coping phq base missingness 8 items}
coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
  mutate(
    phq.missing_only_suicide_item_base = 
      if_else(
        condition = na_per_person_phq_base == 1 & 
          is.na(phq.dead_hurting_thoughts_base_numeric), 
        true = 1,
        false = 0,
        missing = NA_real_
      )
  )

@@

missigness

retrospective
```{r coping ocir retro missingness}
coping.glad.ocir.raw.id <- coping.glad.ocir.raw.id %>%
  mutate(
    na_per_person_ocir_retro =         # variable for NA per person
      rowSums(
        is.na(.[ocir.items_retro])
      )
  )

coping.glad.ocir.raw.id %>%
  freq(na_per_person_ocir_retro, cumul = F) #have a look at the frequency
```

baseline
```{r coping ocir base missingness}
coping.glad.ocir.raw.id <- coping.glad.ocir.raw.id %>%
  mutate(
    na_per_person_ocir_base =         # variable for NA per person
      rowSums(                       
        is.na(.[ocir.items_base])
      )
  )

coping.glad.ocir.raw.id %>%
  freq(na_per_person_ocir_base, cumul = F) #have a look at the frequency
```
